---
title: "Raw mzXML data using Bioconductor's ExperimentHub"
author: "Josie Hayes"
date: '`r format(Sys.Date(), "%B %e, %Y")`'
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Raw mzXML data using Bioconductor's ExperimentHub}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

# Adductomics analysis with Raw mzXML data using Bioconductor's ExperimentHub

Data were produced on a LTQ Orbitrap XL HRMS coupled with a Dionex Ultimate
3000 nanoflow LC system via a Flex Ion nano-electrospray-ionization source 
according to methods in Grigoryan et al (Anal Chem. 2016 Nov 1; 
88(21): 10504–10512.). RAW files were converted to mzXML using ProteoWizard
msConvert.

```{r, eval=FALSE}

msconvert ORB35017raw.RAW --mzXML
msconvert ORB35017raw.RAW --mzXML

```

The other files were produced using the package adductomicsR
```{r, eval=FALSE}
# load the package
library(adductomicsR)
library(adductData)
```

```{r, echo=FALSE}
suppressMessages(suppressWarnings(library(adductomicsR)))
```

rtDevModels.RData can be produced using:
```{r, quiet=T, eval=FALSE}

rtDevModelling(MS2Dir = system.file("extdata", package = "adductData"), 
nCores=4, runOrder = paste0(system.file("extdata", package = "adductomicsR"),
'/runOrder.csv'))

#access the files using ExperimentHub
library(ExperimentHub)
eh  = ExperimentHub()
temp = query(eh, 'adductData')
temp

```

adductQuantResults.RData can be produced using:
```{r, quiet=T, eval=FALSE}

adductQuant(nCores=4, targTable=paste0(system.file("extdata", 
package = "adductomicsR"),'/exampletargTable2.csv'), intStdRtDrift=30, 
rtDevModels=paste0(system.file("extdata", package = "adductData"),
'/rtDevModels.RData'),
filePaths=list.files(system.file("extdata", package = "adductData"),
    pattern=".mzXML", all.files=FALSE,full.names=TRUE),
quantObject=NULL,indivAdduct=NULL,maxPpm=5,minSimScore=0.8,spikeScans=1,
minPeakHeight=100,maxRtDrift=20,maxRtWindow=240,isoWindow=80,
hkPeptide='LVNEVTEFAK', gaussAlpha=16)

#access the files using ExperimentHub
library(ExperimentHub)
eh  = ExperimentHub()
temp = query(eh, 'adductData')
temp

```
